---
title: "Plot Grid Sandbox v5"
author: "Marc Roddis"
date: "7/17/2020"
output: 
  pdf_document:
    toc: true
    number_sections: true
    toc_depth: 4
    df_print: kable
    fig_width: 9
    fig_height: 9
fontsize: 12pt
geometry: margin=1.5in
---

```{r chunk1, include=FALSE}
library(RCurl)
library(tidyverse)
library(styler)
library(gridExtra)
library(cowplot)
library(truncreg)
library(truncnorm)
library(censReg)
load("AllTablesPredsGraphsv18e.Rdata")
load("AllBetaTablesVarySs.RData")
load("AllBetaTablesAll9.RData")
load("PlotAll3CensRegVaryBetaVBM.RData")
load("best6PredsVaryBeta.RData")
load("PlotAll3censRegVaryBeta.RData")
load("p31GridPlotsVaryBetaFV1.RData")
load("p32GridPlotsVarySdFV1.RData")
load("p33GridPlotsVaryCpropFV1.RData")
knitr::opts_chunk$set(echo=FALSE)
```

# Results for the prediction of the annual means $E(Y|A=a)$

All the graphs in this section will shows MSE, squared-bias, or variance on the y-axis and year on the x-axis for the simulated 15-year period.  

We begin by looking at variance of predictions from our best three substitution methods and our best three censored regression methods.  

We will again use $\texttt{best}$ as our gold standard.

## Predictions for different values of $\beta_{A}$

We will begin by using the same parameter values we used in our earlier section "Evaluation of methods for larger absolute values of `beta28year`".  

These parameters are fixed: $cprop = 0.3$,  $\sigma$ = 0.3, whilst $\beta_{A}$ is given four values: -0.02, -0.04, -0.08 and -0.16 respectively. 


We begin by showing graphs of the variance of predictions of $Y$ annual means from our chosen censoring methods.  

A common feature of all these graphs is that they typically have an approximately parabolic "U" shape, with higher variance at each end of the time period than in the middle of the period.   

This is in accordance with our prior expectations because this is generally the case. 


Our first set of four graphs show the variance of $\texttt{censReg1}$ and $\texttt{censReg2}$ methods relative to $\texttt{best}$ method for $\beta_{A}$ equal to -0.02, -0.04, -0.08, -0.16, respectively.   

```{r chunk21a, eval=FALSE}
p31A_cR_var <- plot_all3_censReg_var_beta002_sd03_cprop03_niter10000
p31B_cR_var <- plot_all3_censReg_var_beta004_sd03_cprop03_niter10000
p31C_cR_var <- plot_all3_censReg_var_beta008_sd03_cprop03_niter10000
p31D_cR_var <- plot_all3_censReg_var_beta016_sd03_cprop03_niter10000

# arrange the three plots in a single row
p31_make_grid_3censReg_var_vary_beta <- plot_grid(
  p31A_cR_var + theme(legend.position="none"),
  p31B_cR_var + theme(legend.position="none"),
  p31C_cR_var+ theme(legend.position="none"),
  p31D_cR_var + theme(legend.position="none"),
  align = 'vh',
  labels = c("beta = -0.02", "beta = -0.04", "beta = -0.08", "beta = -0.16"),
  hjust = -1,
  nrow = 2
)

legend_31 <- get_legend(
  p31A_cR_var + 
    guides(color = guide_legend(nrow = 1)) +
    theme(legend.position = "bottom")
)

p31_grid_plot_3censReg_var_vary_beta <- plot_grid(p31_make_grid_3censReg_var_vary_beta, legend_31, ncol = 1, rel_heights = c(1, .1))
```

```{r chunk21b}
p31_grid_plot_3censReg_var_vary_beta
```



Our second set of four graphs show the variance of $\texttt{subst1}$, $\texttt{subst2}$ and $\texttt{subst4}$  methods relative to $\texttt{best}$ method for $\beta_{A}$ equal to -0.02, -0.04, -0.08, -0.16, respectively. 

```{r chunk22a, eval=FALSE}
p31A_S_var <- plot_all_subst_var_beta002_sd03_cprop03_niter10000
p31B_S_var <- plot_all_subst_var_beta004_sd03_cprop03_niter10000
p31C_S_var <- plot_all_subst_var_beta008_sd03_cprop03_niter10000
p31D_S_var <- plot_all_subst_var_beta016_sd03_cprop03_niter10000

# arrange the three plots in a single row
p31_make_grid_subst_var_vary_beta <- plot_grid(
  p31A_S_var + theme(legend.position="none"),
  p31B_S_var + theme(legend.position="none"),
  p31C_S_var+ theme(legend.position="none"),
  p31D_S_var + theme(legend.position="none"),
  align = 'vh',
  labels = c("beta = -0.02", "beta = -0.04", "beta = -0.08", "beta = -0.16"),
  hjust = -1,
  nrow = 2
)

legend_31 <- get_legend(
  p31A_S_var + 
    guides(color = guide_legend(nrow = 1)) +
    theme(legend.position = "bottom")
)

p31_grid_plot_subst_var_vary_beta <- plot_grid(p31_make_grid_subst_var_vary_beta, legend_31, ncol = 1, rel_heights = c(1, .1))
```

```{r chunk22b}
p31_grid_plot_subst_var_vary_beta
```


Our third set of four graphs simply displays the results from the $\texttt{subst2}$, $\texttt{censReg1}$ and $\texttt{best}$ methods together on the same plot, which is displayed below.

```{r chunk23a, eval=FALSE}
p31A_all_var <- plot_all_var_beta002_sd03_cprop03_niter10000
p31B_all_var <- plot_all_var_beta004_sd03_cprop03_niter10000
p31C_all_var <- plot_all_var_beta008_sd03_cprop03_niter10000
p31D_all_var <- plot_all_var_beta016_sd03_cprop03_niter10000

# arrange the three plots in a single row
p31_make_grid_all_var_vary_beta <- plot_grid(
  p31A_all_var + theme(legend.position="none"),
  p31B_all_var + theme(legend.position="none"),
  p31C_all_var+ theme(legend.position="none"),
  p31D_all_var + theme(legend.position="none"),
  align = 'vh',
  labels = c("beta = -0.02", "beta = -0.04", "beta = -0.08", "beta = -0.16"),
  hjust = -1,
  nrow = 2
)

legend_31 <- get_legend(
  p31A_all_var + 
    guides(color = guide_legend(nrow = 1)) +
    theme(legend.position = "bottom")
)

p31_grid_plot_all_var_vary_beta <- plot_grid(p31_make_grid_all_var_vary_beta, legend_31, ncol = 1, rel_heights = c(1, .1))
```

```{r chunk23b}
p31_grid_plot_all_var_vary_beta
```

We will now show graphs of the bias of predictions of $Y$ annual means from our chosen censoring methods.

Our first set of four graphs show the bias of $\texttt{censReg1}$ and $\texttt{censReg2}$ methods relative to $\texttt{best}$ method for $\beta_{A}$ equal to -0.02, -0.04, -0.08, -0.16, respectively.  


```{r chunk24a, eval=FALSE}
p31A_cR_bias <- plot_all3_censReg_bias_beta002_sd03_cprop03_niter10000
p31B_cR_bias <- plot_all3_censReg_bias_beta004_sd03_cprop03_niter10000
p31C_cR_bias <- plot_all3_censReg_bias_beta008_sd03_cprop03_niter10000
p31D_cR_bias <- plot_all3_censReg_bias_beta016_sd03_cprop03_niter10000

# arrange the three plots in a single row
p31_make_grid_3censReg_bias_vary_beta <- plot_grid(
  p31A_cR_bias + theme(legend.position="none"),
  p31B_cR_bias + theme(legend.position="none"),
  p31C_cR_bias+ theme(legend.position="none"),
  p31D_cR_bias + theme(legend.position="none"),
  align = 'vh',
  labels = c("beta = -0.02", "beta = -0.04", "beta = -0.08", "beta = -0.16"),
  hjust = -1,
  nrow = 2
)

legend_31 <- get_legend(
  p31A_cR_bias + 
    guides(color = guide_legend(nrow = 1)) +
    theme(legend.position = "bottom")
)

p31_grid_plot_3censReg_bias_vary_beta <- plot_grid(p31_make_grid_3censReg_bias_vary_beta, legend_31, ncol = 1, rel_heights = c(1, .1))
```

```{r chunk24b}
p31_grid_plot_3censReg_bias_vary_beta
```


Our second set of four graphs show the bias of $\texttt{subst1}$, $\texttt{subst2}$ and $\texttt{subst4}$  methods relative to $\texttt{best}$ method for $\beta_{A}$ equal to -0.02, -0.04, -0.08, -0.16, respectively. 

```{r chunk25a, eval=FALSE}
p31A_S_bias <- plot_all_subst_bias_beta002_sd03_cprop03_niter10000
p31B_S_bias <- plot_all_subst_bias_beta004_sd03_cprop03_niter10000
p31C_S_bias <- plot_all_subst_bias_beta008_sd03_cprop03_niter10000
p31D_S_bias <- plot_all_subst_bias_beta016_sd03_cprop03_niter10000

# arrange the three plots in a single row
p31_make_grid_subst_bias_vary_beta <- plot_grid(
  p31A_S_bias + theme(legend.position="none"),
  p31B_S_bias + theme(legend.position="none"),
  p31C_S_bias+ theme(legend.position="none"),
  p31D_S_bias + theme(legend.position="none"),
  align = 'vh',
  labels = c("beta = -0.02", "beta = -0.04", "beta = -0.08", "beta = -0.16"),
  hjust = -1,
  nrow = 2
)

legend_31 <- get_legend(
  p31A_S_bias + 
    guides(color = guide_legend(nrow = 1)) +
    theme(legend.position = "bottom")
)

p31_grid_plot_subst_bias_vary_beta <- plot_grid(p31_make_grid_subst_bias_vary_beta, legend_31, ncol = 1, rel_heights = c(1, .1))
```

```{r chunk25b}
p31_grid_plot_subst_bias_vary_beta
```

Our third set of four graphs simply displays the results from the $\texttt{subst2}$, $\texttt{censReg1}$ and $\texttt{best}$ methods together on the same plot, which is displayed below.

```{r chunk26a1, eval=FALSE}
p31A_all_bias <- plot_all_bias_beta002_sd03_cprop03_niter10000
p31B_all_bias <- plot_all_bias_beta004_sd03_cprop03_niter10000
p31C_all_bias <- plot_all_bias_beta008_sd03_cprop03_niter10000
p31D_all_bias <- plot_all_bias_beta016_sd03_cprop03_niter10000

# arrange the three plots in a single row
p31_make_grid_all_bias_vary_beta <- plot_grid(
  p31A_all_bias + theme(legend.position="none"),
  p31B_all_bias + theme(legend.position="none"),
  p31C_all_bias+ theme(legend.position="none"),
  p31D_all_bias + theme(legend.position="none"),
  align = 'vh',
  labels = c("beta = -0.02", "beta = -0.04", "beta = -0.08", "beta = -0.16"),
  hjust = -1,
  nrow = 2
)

legend_31 <- get_legend(
  p31A_all_bias + 
    guides(color = guide_legend(nrow = 1)) +
    theme(legend.position = "bottom")
)

p31_grid_plot_all_bias_vary_beta <- plot_grid(p31_make_grid_all_bias_vary_beta, legend_31, ncol = 1, rel_heights = c(1, .1))
```

```{r chunk26a2}
p31_grid_plot_all_bias_vary_beta
```


We will now show graphs of the MSE of predictions of $Y$ annual means from our chosen censoring methods.

Our first set of four graphs show the MSE of $\texttt{censReg1}$ and $\texttt{censReg2}$ methods relative to $\texttt{best}$ method for $\beta_{A}$ equal to -0.02, -0.04, -0.08, -0.16, respectively.   

```{r chunk26b1, eval=FALSE}
p31A_cR_mse <- plot_all3_censReg_mse_beta002_sd03_cprop03_niter10000
p31B_cR_mse <- plot_all3_censReg_mse_beta004_sd03_cprop03_niter10000
p31C_cR_mse <- plot_all3_censReg_mse_beta008_sd03_cprop03_niter10000
p31D_cR_mse <- plot_all3_censReg_mse_beta016_sd03_cprop03_niter10000

# arrange the three plots in a single row
p31_make_grid_3censReg_mse_vary_beta <- plot_grid(
  p31A_cR_mse + theme(legend.position="none"),
  p31B_cR_mse + theme(legend.position="none"),
  p31C_cR_mse+ theme(legend.position="none"),
  p31D_cR_mse + theme(legend.position="none"),
  align = 'vh',
  labels = c("beta = -0.02", "beta = -0.04", "beta = -0.08", "beta = -0.16"),
  hjust = -1,
  nrow = 2
)

legend_31 <- get_legend(
  p31A_cR_mse + 
    guides(color = guide_legend(nrow = 1)) +
    theme(legend.position = "bottom")
)

p31_grid_plot_3censReg_mse_vary_beta <- plot_grid(p31_make_grid_3censReg_mse_vary_beta, legend_31, ncol = 1, rel_heights = c(1, .1))
```

```{r chunk26b2}

p31_grid_plot_3censReg_mse_vary_beta
```


Our second set of four graphs show the MSE of $\texttt{subst1}$, $\texttt{subst2}$ and $\texttt{subst4}$  methods relative to $\texttt{best}$ method for $\beta_{A}$ equal to -0.02, -0.04, -0.08, -0.16, respectively. 

```{r chunk26c1, eval=FALSE}
p31A_S_mse <- plot_all_subst_mse_beta002_sd03_cprop03_niter10000
p31B_S_mse <- plot_all_subst_mse_beta004_sd03_cprop03_niter10000
p31C_S_mse <- plot_all_subst_mse_beta008_sd03_cprop03_niter10000
p31D_S_mse <- plot_all_subst_mse_beta016_sd03_cprop03_niter10000

# arrange the three plots in a single row
p31_make_grid_subst_mse_vary_beta <- plot_grid(
  p31A_S_mse + theme(legend.position="none"),
  p31B_S_mse + theme(legend.position="none"),
  p31C_S_mse+ theme(legend.position="none"),
  p31D_S_mse + theme(legend.position="none"),
  align = 'vh',
  labels = c("beta = -0.02", "beta = -0.04", "beta = -0.08", "beta = -0.16"),
  hjust = -1,
  nrow = 2
)

legend_31 <- get_legend(
  p31A_S_mse + 
    guides(color = guide_legend(nrow = 1)) +
    theme(legend.position = "bottom")
)

p31_grid_plot_subst_mse_vary_beta <- plot_grid(p31_make_grid_subst_mse_vary_beta, legend_31, ncol = 1, rel_heights = c(1, .1))
```

```{r chunk26c2}
p31_grid_plot_subst_mse_vary_beta
```

Our third set of four graphs simply displays the MSE from the $\texttt{subst2}$, $\texttt{censReg1}$ and $\texttt{best}$ methods together on the same plot, which is displayed below.

```{r chunk26d1, eval=FALSE}
p31A_all_mse <- plot_all_mse_beta002_sd03_cprop03_niter10000
p31B_all_mse <- plot_all_mse_beta004_sd03_cprop03_niter10000
p31C_all_mse <- plot_all_mse_beta008_sd03_cprop03_niter10000
p31D_all_mse <- plot_all_mse_beta016_sd03_cprop03_niter10000

# arrange the three plots in a single row
p31_make_grid_all_mse_vary_beta <- plot_grid(
  p31A_all_mse + theme(legend.position="none"),
  p31B_all_mse + theme(legend.position="none"),
  p31C_all_mse+ theme(legend.position="none"),
  p31D_all_mse + theme(legend.position="none"),
  align = 'vh',
  labels = c("beta = -0.02", "beta = -0.04", "beta = -0.08", "beta = -0.16"),
  hjust = -1,
  nrow = 2
)

legend_31 <- get_legend(
  p31A_all_mse + 
    guides(color = guide_legend(nrow = 1)) +
    theme(legend.position = "bottom")
)

p31_grid_plot_all_mse_vary_beta <- plot_grid(p31_make_grid_all_mse_vary_beta, legend_31, ncol = 1, rel_heights = c(1, .1))
```

```{r chunk26d2}
p31_grid_plot_all_mse_vary_beta
```


## Predictions for different values of sd28vs153

For all our predictions in this section, these parameters are fixed: $cprop = 0.3$,  $\beta_{A} = -0.02$, whilst $\sigma$ is given four values: 0.1, 0.3, 0.5 and 0.7 respectively. 


We begin by showing graphs of the variance of predictions of $Y$ annual means from our chosen censoring methods.  

A common feature of all these graphs is that they typically have an approximately parabolic "U" shape, with higher variance at each end of the time period than in the middle of the period.   

This is in accordance with our prior expectations because this is generally the case. 


Our first set of four graphs show the variance of $\texttt{censReg1}$ and $\texttt{censReg2}$ methods relative to $\texttt{best}$ method for $\sigma$ equal to 0.1, 0.3, 0.5, 0.7, respectively.   

```{r chunk28a, eval=FALSE}
p32A_cR2_var <- plot_all_censReg_var_beta002_sd01_cprop03_niter10000
p32B_cR2_var <- plot_all_censReg_var_beta002_sd03_cprop03_niter10000
p32C_cR2_var <- plot_all_censReg_var_beta002_sd05_cprop03_niter10000
p32D_cR2_var <- plot_all_censReg_var_beta002_sd07_cprop03_niter10000

# arrange the three plots in a single row
p32_make_grid_2censReg_var_vary_sd <- plot_grid(
  p32A_cR2_var + theme(legend.position="none"),
  p32B_cR2_var + theme(legend.position="none"),
  p32C_cR2_var+ theme(legend.position="none"),
  p32D_cR2_var + theme(legend.position="none"),
  align = 'vh',
  labels = c("sigma = 0.1", "sigma = 0.3", "sigma = 0.5", "sigma = 0.7"),
  hjust = -1,
  nrow = 2
)

legend_32 <- get_legend(
  p32A_cR2_var + 
    guides(color = guide_legend(nrow = 1)) +
    theme(legend.position = "bottom")
)

p32_grid_plot_2censReg_var_vary_sd <- plot_grid(p32_make_grid_2censReg_var_vary_sd, legend_32, ncol = 1, rel_heights = c(1, .1))
```

```{r chunk28b}
p32_grid_plot_2censReg_var_vary_sd
```


Our second set of four graphs show the variance of $\texttt{subst1}$, $\texttt{subst2}$ and $\texttt{subst4}$  methods relative to $\texttt{best}$ method for $\sigma$ equal to 0.1, 0.3, 0.5, 0.7, respectively.


```{r chunk29a, eval=FALSE}
p32A_S_var <- plot_all_subst_var_beta002_sd01_cprop03_niter10000
p32B_S_var <- plot_all_subst_var_beta002_sd03_cprop03_niter10000
p32C_S_var <- plot_all_subst_var_beta002_sd05_cprop03_niter10000
p32D_S_var <- plot_all_subst_var_beta002_sd07_cprop03_niter10000

# arrange the three plots in a single row
p32_make_grid_subst_var_vary_sd <- plot_grid(
  p32A_S_var + theme(legend.position="none"),
  p32B_S_var + theme(legend.position="none"),
  p32C_S_var+ theme(legend.position="none"),
  p32D_S_var + theme(legend.position="none"),
  align = 'vh',
  labels = c("sigma = 0.1", "sigma = 0.3", "sigma = 0.5", "sigma = 0.7"),
  hjust = -1,
  nrow = 2
)

legend_32 <- get_legend(
  p32A_S_var + 
    guides(color = guide_legend(nrow = 1)) +
    theme(legend.position = "bottom")
)

p32_grid_plot_subst_var_vary_sd <- plot_grid(p32_make_grid_subst_var_vary_sd, legend_32, ncol = 1, rel_heights = c(1, .1))
```

```{r chunk29b}
p32_grid_plot_subst_var_vary_sd
```

Our third set of four graphs simply displays the results from the $\texttt{subst2}$, $\texttt{censReg1}$ and $\texttt{best}$ methods together on the same plot, which is displayed below.

```{r chunk30a, eval=FALSE}
p32A_all_var <- plot_all_var_beta002_sd01_cprop03_niter10000
p32B_all_var <- plot_all_var_beta002_sd03_cprop03_niter10000
p32C_all_var <- plot_all_var_beta002_sd05_cprop03_niter10000
p32D_all_var <- plot_all_var_beta002_sd07_cprop03_niter10000

# arrange the three plots in a single row
p32_make_grid_all_var_vary_sd <- plot_grid(
  p32A_all_var + theme(legend.position="none"),
  p32B_all_var + theme(legend.position="none"),
  p32C_all_var+ theme(legend.position="none"),
  p32D_all_var + theme(legend.position="none"),
  align = 'vh',
  labels = c("sigma = 0.1", "sigma = 0.3", "sigma = 0.5", "sigma = 0.7"),
  hjust = -1,
  nrow = 2
)

legend_32 <- get_legend(
  p32A_all_var + 
    guides(color = guide_legend(nrow = 1)) +
    theme(legend.position = "bottom")
)

p32_grid_plot_all_var_vary_sd <- plot_grid(p32_make_grid_all_var_vary_sd, legend_32, ncol = 1, rel_heights = c(1, .1))
```

```{r chunk30b}
p32_grid_plot_all_var_vary_sd
```


We will now show graphs of the bias of predictions of $Y$ annual means from our chosen censoring methods.

Our first set of four graphs show the bias of $\texttt{censReg1}$ and $\texttt{censReg2}$ methods relative to $\texttt{best}$ method for $\sigma$ equal to 0.1, 0.3, 0.5, 0.7, respectively.   


```{r chunk31a, eval=FALSE}
p32A_2censReg_bias <- plot_all_censReg_bias_beta002_sd01_cprop03_niter10000
p32B_2censReg_bias <- plot_all_censReg_bias_beta002_sd03_cprop03_niter10000
p32C_2censReg_bias <- plot_all_censReg_bias_beta002_sd05_cprop03_niter10000
p32D_2censReg_bias <- plot_all_censReg_bias_beta002_sd07_cprop03_niter10000

# arrange the three plots in a single row
p32_make_grid_2censReg_bias_vary_sd <- plot_grid(
  p32A_2censReg_bias + theme(legend.position="none"),
  p32B_2censReg_bias + theme(legend.position="none"),
  p32C_2censReg_bias+ theme(legend.position="none"),
  p32D_2censReg_bias + theme(legend.position="none"),
  align = 'vh',
  labels = c("sigma = 0.1", "sigma = 0.3", "sigma = 0.5", "sigma = 0.7"),
  hjust = -1,
  nrow = 2
)

legend_32 <- get_legend(
  p32A_2censReg_bias + 
    guides(color = guide_legend(nrow = 1)) +
    theme(legend.position = "bottom")
)

p32_grid_plot_2censReg_bias_vary_sd <- plot_grid(p32_make_grid_2censReg_bias_vary_sd, legend_32, ncol = 1, rel_heights = c(1, .1))
```

```{r chunk31b}
p32_grid_plot_2censReg_bias_vary_sd
```


Our second set of four graphs show the bias of $\texttt{subst1}$, $\texttt{subst2}$ and $\texttt{subst4}$  methods relative to $\texttt{best}$ method for $\sigma$ equal to 0.1, 0.3, 0.5, 0.7, respectively. 

```{r chunk32a, eval=FALSE}
p32A_all_subst_bias <- plot_all_subst_bias_beta002_sd01_cprop03_niter10000
p32B_all_subst_bias <- plot_all_subst_bias_beta002_sd03_cprop03_niter10000
p32C_all_subst_bias <- plot_all_subst_bias_beta002_sd05_cprop03_niter10000
p32D_all_subst_bias <- plot_all_subst_bias_beta002_sd07_cprop03_niter10000

# arrange the three plots in a single row
p32_make_grid_all_subst_bias_vary_sd <- plot_grid(
  p32A_all_subst_bias + theme(legend.position="none"),
  p32B_all_subst_bias + theme(legend.position="none"),
  p32C_all_subst_bias+ theme(legend.position="none"),
  p32D_all_subst_bias + theme(legend.position="none"),
  align = 'vh',
  labels = c("sigma = 0.1", "sigma = 0.3", "sigma = 0.5", "sigma = 0.7"),
  hjust = -1,
  nrow = 2
)

legend_32 <- get_legend(
  p32A_all_subst_bias + 
    guides(color = guide_legend(nrow = 1)) +
    theme(legend.position = "bottom")
)

p32_grid_plot_all_subst_bias_vary_sd <- plot_grid(p32_make_grid_all_subst_bias_vary_sd, legend_32, ncol = 1, rel_heights = c(1, .1))
```

```{r chunk32b}
p32_grid_plot_all_subst_bias_vary_sd
```

Our third set of four graphs simply displays the results from the $\texttt{subst2}$, $\texttt{censReg1}$ and $\texttt{best}$ methods together on the same plot, which is displayed below.

```{r chunk33a, eval=FALSE}
p32A_all_bias <- plot_all_bias_beta002_sd01_cprop03_niter10000
p32B_all_bias <- plot_all_bias_beta002_sd03_cprop03_niter10000
p32C_all_bias <- plot_all_bias_beta002_sd05_cprop03_niter10000
p32D_all_bias <- plot_all_bias_beta002_sd07_cprop03_niter10000

# arrange the three plots in a single row
p32_make_grid_all_bias_vary_sd <- plot_grid(
  p32A_all_bias + theme(legend.position="none"),
  p32B_all_bias + theme(legend.position="none"),
  p32C_all_bias+ theme(legend.position="none"),
  p32D_all_bias + theme(legend.position="none"),
  align = 'vh',
  labels = c("sigma = 0.1", "sigma = 0.3", "sigma = 0.5", "sigma = 0.7"),
  hjust = -1,
  nrow = 2
)

legend_32 <- get_legend(
  p32A_all_bias + 
    guides(color = guide_legend(nrow = 1)) +
    theme(legend.position = "bottom")
)

p32_grid_plot_all_bias_vary_sd <- plot_grid(p32_make_grid_all_bias_vary_sd, legend_32, ncol = 1, rel_heights = c(1, .1))
```

```{r chunk33b}
p32_grid_plot_all_bias_vary_sd
```


We will now show graphs of the MSE of predictions of $Y$ annual means from our chosen censoring methods.

Our first set of four graphs show the MSE of $\texttt{censReg1}$ and $\texttt{censReg2}$ methods relative to $\texttt{best}$ method for $\sigma$ equal to 0.1, 0.3, 0.5, 0.7, respectively.   

```{r chunk33a, eval=FALSE}
p32A_2censReg_mse <- plot_all_censReg_mse_beta002_sd01_cprop03_niter10000
p32B_2censReg_mse <- plot_all_censReg_mse_beta002_sd03_cprop03_niter10000
p32C_2censReg_mse <- plot_all_censReg_mse_beta002_sd05_cprop03_niter10000
p32D_2censReg_mse <- plot_all_censReg_mse_beta002_sd07_cprop03_niter10000

# arrange the three plots in a single row
p32_make_grid_2censReg_mse_vary_sd <- plot_grid(
  p32A_2censReg_mse + theme(legend.position="none"),
  p32B_2censReg_mse + theme(legend.position="none"),
  p32C_2censReg_mse+ theme(legend.position="none"),
  p32D_2censReg_mse + theme(legend.position="none"),
  align = 'vh',
  labels = c("sigma = 0.1", "sigma = 0.3", "sigma = 0.5", "sigma = 0.7"),
  hjust = -1,
  nrow = 2
)

legend_32 <- get_legend(
  p32A_2censReg_mse + 
    guides(color = guide_legend(nrow = 1)) +
    theme(legend.position = "bottom")
)

p32_grid_plot_2censReg_mse_vary_sd <- plot_grid(p32_make_grid_2censReg_mse_vary_sd, legend_32, ncol = 1, rel_heights = c(1, .1))
```

```{r chunk33b}
p32_grid_plot_2censReg_mse_vary_sd
```



Our second set of four graphs show the MSE of $\texttt{subst1}$, $\texttt{subst2}$ and $\texttt{subst4}$  methods relative to $\texttt{best}$ method for $\sigma$ equal to 0.1, 0.3, 0.5, 0.7, respectively. 


```{r chunk33a, eval=FALSE}
p32A_all_subst_mse <- plot_all_subst_mse_beta002_sd01_cprop03_niter10000
p32B_all_subst_mse <- plot_all_subst_mse_beta002_sd03_cprop03_niter10000
p32C_all_subst_mse <- plot_all_subst_mse_beta002_sd05_cprop03_niter10000
p32D_all_subst_mse <- plot_all_subst_mse_beta002_sd07_cprop03_niter10000

# arrange the three plots in a single row
p32_make_grid_all_subst_mse_vary_sd <- plot_grid(
  p32A_all_subst_mse + theme(legend.position="none"),
  p32B_all_subst_mse + theme(legend.position="none"),
  p32C_all_subst_mse+ theme(legend.position="none"),
  p32D_all_subst_mse + theme(legend.position="none"),
  align = 'vh',
  labels = c("sigma = 0.1", "sigma = 0.3", "sigma = 0.5", "sigma = 0.7"),
  hjust = -1,
  nrow = 2
)

legend_32 <- get_legend(
  p32A_all_subst_mse + 
    guides(color = guide_legend(nrow = 1)) +
    theme(legend.position = "bottom")
)

p32_grid_plot_all_subst_mse_vary_sd <- plot_grid(p32_make_grid_all_subst_mse_vary_sd, legend_32, ncol = 1, rel_heights = c(1, .1))
```

```{r chunk33b}
p32_grid_plot_all_subst_mse_vary_sd
```

Our third set of four graphs simply displays the MSE from the $\texttt{subst2}$, $\texttt{censReg1}$ and $\texttt{best}$ methods together on the same plot, which is displayed below.

```{r chunk34a, eval=FALSE}
p32A_all_mse <- plot_all_mse_beta002_sd01_cprop03_niter10000
p32B_all_mse <- plot_all_mse_beta002_sd03_cprop03_niter10000
p32C_all_mse <- plot_all_mse_beta002_sd05_cprop03_niter10000
p32D_all_mse <- plot_all_mse_beta002_sd07_cprop03_niter10000

# arrange the three plots in a single row
p32_make_grid_all_mse_vary_sd <- plot_grid(
  p32A_all_mse + theme(legend.position="none"),
  p32B_all_mse + theme(legend.position="none"),
  p32C_all_mse+ theme(legend.position="none"),
  p32D_all_mse + theme(legend.position="none"),
  align = 'vh',
  labels = c("sigma = 0.1", "sigma = 0.3", "sigma = 0.5", "sigma = 0.7"),
  hjust = -1,
  nrow = 2
)

legend_32 <- get_legend(
  p32A_all_mse + 
    guides(color = guide_legend(nrow = 1)) +
    theme(legend.position = "bottom")
)

p32_grid_plot_all_mse_vary_sd <- plot_grid(p32_make_grid_all_mse_vary_sd, legend_32, ncol = 1, rel_heights = c(1, .1))
```

```{r chunk34b}
p32_grid_plot_all_mse_vary_sd
```


## Predictions for different values of $cprop$

For all our predictions in this section, these parameters are fixed: $\sigma = 0.5$,  $\beta_{A} = -0.02$, whilst $cprop$ is given the four values: 0.1, 0.3, 0.5 and 0.7 respectively. 

We begin by showing graphs of the variance of predictions of $Y$ annual means from our chosen censoring methods.

Our first set of four graphs show the variance of $\texttt{censReg1}$ and $\texttt{censReg2}$ methods relative to $\texttt{best}$ method for $cprop$ equal to 0.1, 0.3, 0.5, 0.7, respectively.   



Our second set of four graphs show the variance of $\texttt{subst1}$, $\texttt{subst2}$ and $\texttt{subst4}$  methods relative to $\texttt{best}$ method for $cprop$ equal to 0.1, 0.3, 0.5, 0.7, respectively.

```{r chunk36, eval=FALSE}
plot_grid(plot_all_subst_var_beta002_sd05_cprop01_niter10000, plot_all_subst_var_beta002_sd05_cprop03_niter10000, plot_all_subst_var_beta002_sd05_cprop05_niter10000, plot_all_subst_var_beta002_sd05_cprop07_niter10000, labels = "AUTO")
```

Our third set of four graphs simply displays the results from the $\texttt{subst2}$, $\texttt{censReg1}$ and $\texttt{best}$ methods together on the same plot, which is displayed below. 

```{r chunk37, eval=FALSE}
plot_grid(plot_all_var_beta002_sd05_cprop01_niter10000, plot_all_var_beta002_sd05_cprop03_niter10000, plot_all_var_beta002_sd05_cprop05_niter10000, plot_all_var_beta002_sd05_cprop07_niter10000, labels = "AUTO")
```


We will now show graphs of the bias of predictions of $Y$ annual means from our chosen censoring methods.

Our first set of four graphs show the bias of $\texttt{censReg1}$ and $\texttt{censReg2}$ methods relative to $\texttt{best}$ method for $cprop$ equal to 0.1, 0.3, 0.5, 0.7, respectively.   

```{r chunk38, eval=FALSE}
plot_grid(plot_all_censReg_bias_beta002_sd05_cprop01_niter10000, plot_all_censReg_bias_beta002_sd05_cprop03_niter10000, plot_all_censReg_bias_beta002_sd05_cprop05_niter10000, plot_all_censReg_bias_beta002_sd05_cprop07_niter10000, labels = "AUTO")
```

Our second set of four graphs show the bias of $\texttt{subst1}$, $\texttt{subst2}$ and $\texttt{subst4}$  methods relative to $\texttt{best}$ method for $cprop$ equal to 0.1, 0.3, 0.5, 0.7, respectively. 

```{r chunk39, eval=FALSE}
plot_grid(plot_all_subst_bias_beta002_sd05_cprop01_niter10000, plot_all_subst_bias_beta002_sd05_cprop03_niter10000, plot_all_subst_bias_beta002_sd05_cprop05_niter10000, plot_all_subst_bias_beta002_sd05_cprop07_niter10000, labels = "AUTO")
```

Our third set of four graphs simply displays the results from the $\texttt{subst2}$, $\texttt{censReg1}$ and $\texttt{best}$ methods together on the same plot, which is displayed below.

```{r chunk40a, eval=FALSE}
plot_grid(plot_all_bias_beta002_sd05_cprop01_niter10000, plot_all_bias_beta002_sd05_cprop03_niter10000, plot_all_bias_beta002_sd05_cprop05_niter10000, plot_all_bias_beta002_sd05_cprop07_niter10000, labels = "AUTO")
```


We will now show graphs of the MSE of predictions of $Y$ annual means from our chosen censoring methods.

Our first set of four graphs show the MSE of $\texttt{censReg1}$ and $\texttt{censReg2}$ methods relative to $\texttt{best}$ method for $cprop$ equal to 0.1, 0.3, 0.5, 0.7, respectively.   

```{r chunk40b, eval=FALSE}
plot_grid(plot_all_censReg_mse_beta002_sd05_cprop01_niter10000, plot_all_censReg_mse_beta002_sd05_cprop03_niter10000, plot_all_censReg_mse_beta002_sd05_cprop05_niter10000, plot_all_censReg_mse_beta002_sd05_cprop07_niter10000, labels = "AUTO")
```

Our second set of four graphs show the MSE of $\texttt{subst1}$, $\texttt{subst2}$ and $\texttt{subst4}$  methods relative to $\texttt{best}$ method for $cprop$ equal to 0.1, 0.3, 0.5, 0.7, respectively. 

```{r chunk40c, eval=FALSE}
plot_grid(plot_all_subst_mse_beta002_sd05_cprop01_niter10000, plot_all_subst_mse_beta002_sd05_cprop03_niter10000, plot_all_subst_mse_beta002_sd05_cprop05_niter10000, plot_all_subst_mse_beta002_sd05_cprop07_niter10000, labels = "AUTO")
```

Our third set of four graphs simply displays the MSE from the $\texttt{subst2}$, $\texttt{censReg1}$ and $\texttt{best}$ methods together on the same plot, which is displayed below.

```{r chunk40d, eval=FALSE}
plot_grid(plot_all_mse_beta002_sd05_cprop01_niter10000, plot_all_mse_beta002_sd05_cprop03_niter10000, plot_all_mse_beta002_sd05_cprop05_niter10000, plot_all_mse_beta002_sd05_cprop07_niter10000, labels = "AUTO")
```







```{r chunk35a, eval=FALSE}
p33A_cR2_var <- plot_all_censReg_var_beta002_sd05_cprop01_niter10000
p33B_cR2_var <- plot_all_censReg_var_beta002_sd05_cprop03_niter10000
p33C_cR2_var <- plot_all_censReg_var_beta002_sd05_cprop05_niter10000
p33D_cR2_var <- plot_all_censReg_var_beta002_sd05_cprop07_niter10000

# arrange the three plots in a single row
p33_make_grid_2censReg_var_vary_cprop <- plot_grid(
  p33A_cR2_var + theme(legend.position="none"),
  p33B_cR2_var + theme(legend.position="none"),
  p33C_cR2_var+ theme(legend.position="none"),
  p33D_cR2_var + theme(legend.position="none"),
  align = 'vh',
  labels = c("cprop = 0.1", "cprop = 0.3", "cprop = 0.5", "cprop = 0.7"),
  hjust = -1,
  nrow = 2
)

legend_33 <- get_legend(
  p33A_cR2_var + 
    guides(color = guide_legend(nrow = 1)) +
    theme(legend.position = "bottom")
)

p33_grid_plot_2censReg_var_vary_cprop <- plot_grid(p33_make_grid_2censReg_var_vary_cprop, legend_33, ncol = 1, rel_heights = c(1, .1))
```

```{r chunk35b}
p33_grid_plot_2censReg_var_vary_cprop
```


Our second set of four graphs show the variance of $\texttt{subst1}$, $\texttt{subst2}$ and $\texttt{subst4}$  methods relative to $\texttt{best}$ method for $cprop$ equal to 0.1, 0.3, 0.5, 0.7, respectively.


```{r chunk36a, eval=FALSE}
p33A_S_var <- plot_all_subst_var_beta002_sd05_cprop01_niter10000
p33B_S_var <- plot_all_subst_var_beta002_sd05_cprop03_niter10000
p33C_S_var <- plot_all_subst_var_beta002_sd05_cprop05_niter10000
p33D_S_var <- plot_all_subst_var_beta002_sd05_cprop07_niter10000

# arrange the three plots in a single row
p33_make_grid_subst_var_vary_cprop <- plot_grid(
  p33A_S_var + theme(legend.position="none"),
  p33B_S_var + theme(legend.position="none"),
  p33C_S_var+ theme(legend.position="none"),
  p33D_S_var + theme(legend.position="none"),
  align = 'vh',
  labels = c("cprop = 0.1", "cprop = 0.3", "cprop = 0.5", "cprop = 0.7"),
  hjust = -1,
  nrow = 2
)

legend_33 <- get_legend(
  p33A_S_var + 
    guides(color = guide_legend(nrow = 1)) +
    theme(legend.position = "bottom")
)

p33_grid_plot_all_subst_var_vary_cprop <- plot_grid(p33_make_grid_subst_var_vary_cprop, legend_33, ncol = 1, rel_heights = c(1, .1))
```

```{r chunk36b}
p33_grid_plot_all_subst_var_vary_cprop
```

Our third set of four graphs simply displays the results from the $\texttt{subst2}$, $\texttt{censReg1}$ and $\texttt{best}$ methods together on the same plot, which is displayed below.

```{r chunk37a, eval=FALSE}
p33A_all_var <- plot_all_var_beta002_sd05_cprop01_niter10000
p33B_all_var <- plot_all_var_beta002_sd05_cprop03_niter10000
p33C_all_var <- plot_all_var_beta002_sd05_cprop05_niter10000
p33D_all_var <- plot_all_var_beta002_sd05_cprop07_niter10000

# arrange the three plots in a single row
p33_make_grid_all_var_vary_cprop <- plot_grid(
  p33A_all_var + theme(legend.position="none"),
  p33B_all_var + theme(legend.position="none"),
  p33C_all_var+ theme(legend.position="none"),
  p33D_all_var + theme(legend.position="none"),
  align = 'vh',
  labels = c("cprop = 0.1", "cprop = 0.3", "cprop = 0.5", "cprop = 0.7"),
  hjust = -1,
  nrow = 2
)

legend_33 <- get_legend(
  p33A_all_var + 
    guides(color = guide_legend(nrow = 1)) +
    theme(legend.position = "bottom")
)

p33_grid_plot_all_var_vary_cprop <- plot_grid(p33_make_grid_all_var_vary_cprop, legend_33, ncol = 1, rel_heights = c(1, .1))
```

```{r chunk37b}
p33_grid_plot_all_var_vary_cprop
```


We will now show graphs of the bias of predictions of $Y$ annual means from our chosen censoring methods.

Our first set of four graphs show the bias of $\texttt{censReg1}$ and $\texttt{censReg2}$ methods relative to $\texttt{best}$ method for $cprop$ equal to 0.1, 0.3, 0.5, 0.7, respectively.   


```{r chunk38a, eval=FALSE}
p33A_cR2_bias <- plot_all_censReg_bias_beta002_sd05_cprop01_niter10000
p33B_cR2_bias <- plot_all_censReg_bias_beta002_sd05_cprop03_niter10000
p33C_cR2_bias <- plot_all_censReg_bias_beta002_sd05_cprop05_niter10000
p33D_cR2_bias <- plot_all_censReg_bias_beta002_sd05_cprop07_niter10000

# arrange the three plots in a single row
p33_make_grid_2censReg_bias_vary_cprop <- plot_grid(
  p33A_cR2_bias + theme(legend.position="none"),
  p33B_cR2_bias + theme(legend.position="none"),
  p33C_cR2_bias+ theme(legend.position="none"),
  p33D_cR2_bias + theme(legend.position="none"),
  align = 'vh',
  labels = c("cprop = 0.1", "cprop = 0.3", "cprop = 0.5", "cprop = 0.7"),
  hjust = -1,
  nrow = 2
)

legend_33 <- get_legend(
  p33A_cR2_bias + 
    guides(color = guide_legend(nrow = 1)) +
    theme(legend.position = "bottom")
)

p33_grid_plot_2censReg_bias_vary_cprop <- plot_grid(p33_make_grid_2censReg_bias_vary_cprop, legend_33, ncol = 1, rel_heights = c(1, .1))
```

```{r chunk38b}
p33_grid_plot_2censReg_bias_vary_cprop
```


Our second set of four graphs show the bias of $\texttt{subst1}$, $\texttt{subst2}$ and $\texttt{subst4}$  methods relative to $\texttt{best}$ method for $cprop$ equal to 0.1, 0.3, 0.5, 0.7, respectively. 

```{r chunk39a, eval=FALSE}
p33A_all_subst_bias <- plot_all_subst_bias_beta002_sd05_cprop01_niter10000
p33B_all_subst_bias <- plot_all_subst_bias_beta002_sd05_cprop03_niter10000
p33C_all_subst_bias <- plot_all_subst_bias_beta002_sd05_cprop05_niter10000
p33D_all_subst_bias <- plot_all_subst_bias_beta002_sd05_cprop07_niter10000

# arrange the three plots in a single row
p33_make_grid_all_subst_bias_vary_cprop <- plot_grid(
  p33A_all_subst_bias + theme(legend.position="none"),
  p33B_all_subst_bias + theme(legend.position="none"),
  p33C_all_subst_bias+ theme(legend.position="none"),
  p33D_all_subst_bias + theme(legend.position="none"),
  align = 'vh',
  labels = c("cprop = 0.1", "cprop = 0.3", "cprop = 0.5", "cprop = 0.7"),
  hjust = -1,
  nrow = 2
)

legend_33 <- get_legend(
  p33A_all_subst_bias + 
    guides(color = guide_legend(nrow = 1)) +
    theme(legend.position = "bottom")
)

p33_grid_plot_all_subst_bias_vary_cprop <- plot_grid(p33_make_grid_all_subst_bias_vary_cprop, legend_33, ncol = 1, rel_heights = c(1, .1))
```

```{r chunk39b}
p33_grid_plot_all_subst_bias_vary_cprop
```

Our third set of four graphs simply displays the results from the $\texttt{subst2}$, $\texttt{censReg1}$ and $\texttt{best}$ methods together on the same plot, which is displayed below.

```{r chunk40a, eval=FALSE}
p33A_all_bias <- plot_all_bias_beta002_sd05_cprop01_niter10000
p33B_all_bias <- plot_all_bias_beta002_sd05_cprop03_niter10000
p33C_all_bias <- plot_all_bias_beta002_sd05_cprop05_niter10000
p33D_all_bias <- plot_all_bias_beta002_sd05_cprop07_niter10000

# arrange the three plots in a single row
p33_make_grid_all_bias_vary_cprop <- plot_grid(
  p33A_all_bias + theme(legend.position="none"),
  p33B_all_bias + theme(legend.position="none"),
  p33C_all_bias+ theme(legend.position="none"),
  p33D_all_bias + theme(legend.position="none"),
  align = 'vh',
  labels = c("cprop = 0.1", "cprop = 0.3", "cprop = 0.5", "cprop = 0.7"),
  hjust = -1,
  nrow = 2
)

legend_33 <- get_legend(
  p33A_all_bias + 
    guides(color = guide_legend(nrow = 1)) +
    theme(legend.position = "bottom")
)

p33_grid_plot_all_bias_vary_cprop <- plot_grid(p33_make_grid_all_bias_vary_cprop, legend_33, ncol = 1, rel_heights = c(1, .1))
```

```{r chunk40b}
p33_grid_plot_all_bias_vary_cprop
```


We will now show graphs of the MSE of predictions of $Y$ annual means from our chosen censoring methods.

Our first set of four graphs show the MSE of $\texttt{censReg1}$ and $\texttt{censReg2}$ methods relative to $\texttt{best}$ method for $cprop$ equal to 0.1, 0.3, 0.5, 0.7, respectively.   

```{r chunk41a, eval=FALSE}
p33A_2censReg_mse <- plot_all_censReg_var_beta002_sd05_cprop01_niter10000
p33B_2censReg_mse <- plot_all_censReg_var_beta002_sd05_cprop03_niter10000
p33C_2censReg_mse <- plot_all_censReg_var_beta002_sd05_cprop05_niter10000
p33D_2censReg_mse <- plot_all_censReg_var_beta002_sd05_cprop07_niter10000

# arrange the three plots in a single row
p33_make_grid_2censReg_mse_vary_cprop <- plot_grid(
  p33A_2censReg_mse + theme(legend.position="none"),
  p33B_2censReg_mse + theme(legend.position="none"),
  p33C_2censReg_mse+ theme(legend.position="none"),
  p33D_2censReg_mse + theme(legend.position="none"),
  align = 'vh',
  labels = c("cprop = 0.1", "cprop = 0.3", "cprop = 0.5", "cprop = 0.7"),
  hjust = -1,
  nrow = 2
)

legend_33 <- get_legend(
  p33A_2censReg_mse + 
    guides(color = guide_legend(nrow = 1)) +
    theme(legend.position = "bottom")
)

p33_grid_plot_2censReg_mse_vary_cprop <- plot_grid(p33_make_grid_2censReg_mse_vary_cprop, legend_33, ncol = 1, rel_heights = c(1, .1))
```

```{r chunk41b}
p33_grid_plot_2censReg_mse_vary_cprop
```



Our second set of four graphs show the MSE of $\texttt{subst1}$, $\texttt{subst2}$ and $\texttt{subst4}$  methods relative to $\texttt{best}$ method for $cprop$ equal to 0.1, 0.3, 0.5, 0.7, respectively. 


```{r chunk42a, eval=FALSE}
p33A_all_subst_mse <- plot_all_subst_mse_beta002_sd05_cprop01_niter10000
p33B_all_subst_mse <- plot_all_subst_mse_beta002_sd05_cprop03_niter10000
p33C_all_subst_mse <- plot_all_subst_mse_beta002_sd05_cprop05_niter10000
p33D_all_subst_mse <- plot_all_subst_mse_beta002_sd05_cprop07_niter10000

# arrange the three plots in a single row
p33_make_grid_all_subst_mse_vary_cprop <- plot_grid(
  p33A_all_subst_mse + theme(legend.position="none"),
  p33B_all_subst_mse + theme(legend.position="none"),
  p33C_all_subst_mse+ theme(legend.position="none"),
  p33D_all_subst_mse + theme(legend.position="none"),
  align = 'vh',
  labels = c("cprop = 0.1", "cprop = 0.3", "cprop = 0.5", "cprop = 0.7"),
  hjust = -1,
  nrow = 2
)

legend_33 <- get_legend(
  p33A_all_subst_mse + 
    guides(color = guide_legend(nrow = 1)) +
    theme(legend.position = "bottom")
)

p33_grid_plot_all_subst_mse_vary_cprop <- plot_grid(p33_make_grid_all_subst_mse_vary_cprop, legend_33, ncol = 1, rel_heights = c(1, .1))
```

```{r chunk42b}
p33_grid_plot_all_subst_mse_vary_cprop
```

Our third set of four graphs simply displays the MSE from the $\texttt{subst2}$, $\texttt{censReg1}$ and $\texttt{best}$ methods together on the same plot, which is displayed below.

```{r chunk43a, eval=FALSE}
p33A_all_mse <- plot_all_mse_beta002_sd05_cprop01_niter10000
p33B_all_mse <- plot_all_mse_beta002_sd05_cprop03_niter10000
p33C_all_mse <- plot_all_mse_beta002_sd05_cprop05_niter10000
p33D_all_mse <- plot_all_mse_beta002_sd05_cprop07_niter10000

# arrange the three plots in a single row
p33_make_grid_all_mse_vary_cprop <- plot_grid(
  p33A_all_mse + theme(legend.position="none"),
  p33B_all_mse + theme(legend.position="none"),
  p33C_all_mse+ theme(legend.position="none"),
  p33D_all_mse + theme(legend.position="none"),
  align = 'vh',
  labels = c("cprop = 0.1", "cprop = 0.3", "cprop = 0.5", "cprop = 0.7"),
  hjust = -1,
  nrow = 2
)

legend_33 <- get_legend(
  p33A_all_mse + 
    guides(color = guide_legend(nrow = 1)) +
    theme(legend.position = "bottom")
)

p33_grid_plot_all_mse_vary_cprop <- plot_grid(p33_make_grid_all_mse_vary_cprop, legend_33, ncol = 1, rel_heights = c(1, .1))
```

```{r chunk43b}
p33_grid_plot_all_mse_vary_cprop
```











## Predictions for low-low, high-low, low-high, high-high values of $\{\sigma,cprop\}$

We will now use the same sets of parameter values that we used in our earlier section "Selection of censoring methods for further study".  

Concretely: $\beta_{A} = -0.02$ is held fixed, whilst a "low" and a "high" value for each of $cprop$ and $\sigma$ are used.  

Concretely: $\{(0.1, 0.1), (0.7, 0.1), (0.1, 0.5), (0.7, 0.5)\}$ were used for $\{cprop, \sigma\}$ respectively.


We begin by showing graphs of the variance of predictions of $Y$ annual means from our chosen censoring methods.

Our first set of four graphs show the variance of $\texttt{censReg1}$ and $\texttt{censReg2}$ methods relative to $\texttt{best}$ method for ($\sigma$, $cprop$) equal to (0.1, 0.1), (0.1, 0.7), (0.7, 0.1) and (0.7, 0.7), respectively.   

```{r chunk44, eval=FALSE}
plot_grid(plot_all_censReg_var_beta002_sd01_cprop01_niter10000, plot_all_censReg_var_beta002_sd01_cprop07_niter10000, plot_all_censReg_var_beta002_sd07_cprop01_niter10000, plot_all_censReg_var_beta002_sd07_cprop07_niter10000, labels = "AUTO")
```

Our second set of four graphs show the variance of $\texttt{subst1}$, $\texttt{subst2}$ and $\texttt{subst4}$  methods relative to $\texttt{best}$ method for ($\sigma$, $cprop$) equal to (0.1, 0.1), (0.1, 0.7), (0.7, 0.1) and (0.7, 0.7), respectively.   

```{r chunk45, eval=FALSE}
plot_grid(plot_all_subst_var_beta002_sd01_cprop01_niter10000, plot_all_subst_var_beta002_sd01_cprop07_niter10000, plot_all_subst_var_beta002_sd07_cprop01_niter10000, plot_all_subst_var_beta002_sd07_cprop07_niter10000, labels = "AUTO")
```

Our third set of four graphs simply displays the results from the $\texttt{subst2}$, $\texttt{censReg1}$ and $\texttt{best}$ methods together on the same plot, which is displayed below.

```{r chunk46, eval=FALSE}
plot_grid(plot_all_var_beta002_sd01_cprop01_niter10000, plot_all_var_beta002_sd01_cprop07_niter10000, plot_all_var_beta002_sd07_cprop01_niter10000, plot_all_var_beta002_sd07_cprop07_niter10000, labels = "AUTO")
```


We will now show graphs of the bias of predictions of $Y$ annual means from our chosen censoring methods.

Our first set of four graphs show the bias of $\texttt{censReg1}$ and $\texttt{censReg2}$ methods relative to $\texttt{best}$ method for ($\sigma$, $cprop$) equal to (0.1, 0.1), (0.1, 0.7), (0.7, 0.1) and (0.7, 0.7), respectively.      

```{r chunk47, eval=FALSE}
plot_grid(plot_all_censReg_bias_beta002_sd01_cprop01_niter10000, plot_all_censReg_bias_beta002_sd01_cprop07_niter10000, plot_all_censReg_bias_beta002_sd07_cprop01_niter10000, plot_all_censReg_bias_beta002_sd07_cprop07_niter10000, labels = "AUTO")
```

Our second set of four graphs show the bias of $\texttt{subst1}$, $\texttt{subst2}$ and $\texttt{subst4}$  methods relative to $\texttt{best}$ method for ($\sigma$, $cprop$) equal to (0.1, 0.1), (0.1, 0.7), (0.7, 0.1) and (0.7, 0.7), respectively.    

```{r chunk48, eval=FALSE}
plot_grid(plot_all_subst_bias_beta002_sd01_cprop01_niter10000, plot_all_subst_bias_beta002_sd01_cprop07_niter10000, plot_all_subst_bias_beta002_sd07_cprop01_niter10000, plot_all_subst_bias_beta002_sd07_cprop07_niter10000, labels = "AUTO")
```

Our third set of four graphs simply displays the results from the $\texttt{subst2}$, $\texttt{censReg1}$ and $\texttt{best}$ methods together on the same plot, which is displayed below.

```{r chunk49, eval=FALSE}
plot_grid(plot_all_bias_beta002_sd01_cprop01_niter10000, plot_all_bias_beta002_sd01_cprop07_niter10000, plot_all_bias_beta002_sd07_cprop01_niter10000, plot_all_bias_beta002_sd07_cprop07_niter10000, labels = "AUTO")
```


We will now show graphs of the MSE of predictions of $Y$ annual means from our chosen censoring methods.

Our first set of four graphs show the MSE of $\texttt{censReg1}$ and $\texttt{censReg2}$ methods relative to $\texttt{best}$ method for ($\sigma$, $cprop$) equal to (0.1, 0.1), (0.1, 0.7), (0.7, 0.1) and (0.7, 0.7), respectively.      

```{r chunk50, eval=FALSE}
plot_grid(plot_all_censReg_mse_beta002_sd01_cprop01_niter10000, plot_all_censReg_mse_beta002_sd01_cprop07_niter10000, plot_all_censReg_mse_beta002_sd07_cprop01_niter10000, plot_all_censReg_mse_beta002_sd07_cprop07_niter10000, labels = "AUTO")
```

Our second set of four graphs show the MSE of $\texttt{subst1}$, $\texttt{subst2}$ and $\texttt{subst4}$  methods relative to $\texttt{best}$ method for ($\sigma$, $cprop$) equal to (0.1, 0.1), (0.1, 0.7), (0.7, 0.1) and (0.7, 0.7), respectively.    

```{r chunk51, eval=FALSE}
plot_grid(plot_all_subst_mse_beta002_sd01_cprop01_niter10000, plot_all_subst_mse_beta002_sd01_cprop07_niter10000, plot_all_subst_mse_beta002_sd07_cprop01_niter10000, plot_all_subst_mse_beta002_sd07_cprop07_niter10000, labels = "AUTO")
```

Our third set of four graphs simply displays the MSE from the $\texttt{subst2}$, $\texttt{censReg1}$ and $\texttt{best}$ methods together on the same plot, which is displayed below.

```{r chunk52, eval=FALSE}
plot_grid(plot_all_mse_beta002_sd01_cprop01_niter10000, plot_all_mse_beta002_sd01_cprop07_niter10000, plot_all_mse_beta002_sd07_cprop01_niter10000, plot_all_mse_beta002_sd07_cprop07_niter10000, labels = "AUTO")



```

